\begin{FrenchAbstract}
%
%
Ce manuscrit présente différentes études expérimentales qui s'inscrivent dans le cadre d'une recherche dont l'objectif est la réalisation d'un \sotosay{\lat} continu et intense.
Nous commençons par décrire le \setup qui permet de mettre en \oe uvre le \rpef d'un \jatgm.
Le gain observé, d'un facteur~$10$, sur la \ddedp est limité par la dynamique collisionnelle du \j. 

Pour améliorer les performances du refroidissement, il apparaît nécessaire de développer de nouvelles techniques expérimentales.
Nous détaillons ainsi une nouvelle méthode d'évaporation très efficace, par mise en contact des atomes du jet avec une surface matérielle.

Les autres études menées portent sur la production et la manipulation de \natufs. 
La première consiste à ralentir des \pats par réflexion sur un \mimamo. 
La seconde permet la capture et le refroidissement d'une succession de \pats dans un \tpIP.
La dernière technique met en \oe uvre un \pd, produit par un \fl de forte puissance, afin de produire puis de mettre en mouvement des \patufs très denses. 
Nous présentons enfin un nouveau protocole d'imagerie par absorption donnant accès à des mesures quantitatives et précises des \nats optiquement épais que nous produisons.
%
%
\KeyWords{\lat, évaporation, \jat, \gm, \pat, \mima, Démon de Maxwell, \tpIP, \pd, transport non-adiabatique, \ipa.}
\end{FrenchAbstract}


\begin{EnglishAbstract}
%
%
This manuscript presents various studies for an experiment aimed at achieving a continuous and intense \sotosay{atom laser}. We start by describing the experimental setup that allows us to implement the forced evaporative cooling of a magnetically guided atomic beam. The observed gain, by a factor of~10, on the phase space density is limited by the collisional dynamics. 

To improve the performance of evaporative cooling, it appears to be necessary to develop new experimental techniques.
We describe a method of evaporation of the beam, by contact with a material surface.

The other studies address the production and manipulation of ultra-cold atomic clouds.
The first consists in the slowing down of atomic packets by reflection on a moving magnetic mirror. The second allows the capture and cooling of a succession of packets in a train of Ioffe-Pritchard's traps.
The last technique relies on a dipolar trap, produced by a powerful laser beam, in order to produce and then to set in motion dense ultra-cold clouds. We finally report on a new absorption imaging protocol which provides to quantitative accurate measurements for the optically thick atomic clouds that we can produce.
%
%
\KeyWords{atom laser, evaporation, atomic beam, magnetic guide, atomic packet, magnetic mirror, Maxwell's Demon, train of Ioffe-Pritchard's traps, dipole trap, non-adiabatic transport, absorption imaging.}
\end{EnglishAbstract}
